---
title: "data-analysis"
author: "Meng Ye"
date: "2025-03-09"
output:
  html_document: default
  word_document: default
  pdf_document: default
---

## Introduction 

The current version re-run the codes of the data analysis. 
```{r contr}
# environment setup to run ordered logit properly
options(contrasts = rep("contr.treatment", 2))
```

### Load packages 

```{r load package, message=FALSE, warning=FALSE}
library(tidyverse) # package for data cleaning and plotting
library(readxl)
library(modelsummary)
library(ordinal) # package for ordinal logit regression
library(brant) # brant test for the parallel assumption for ordered logit
library(MASS) # models that work with the brant test
library(broom) # extracting model summary as data frame
library(modelsummary) # deriving model tables
library(scales) # label percent
library(lubridate) # working with dates
library(marginaleffects) #to calculate marginal effects
library(gt) # to format tables
library(here) # work with directory
set.seed(5432)
```



## Merging CQC and financial data 


```{r import data 0, message=FALSE, warning=FALSE}
# import location level full data
rating<- read_csv(here("cleaned_data","cic_all_ratings_2019.csv"))
```


```{r import data finance, message=FALSE, warning=FALSE}
finance <- read_csv(here("cleaned_data","cls_finance_2025.csv"))
```


```{r}
finance1 <- finance %>% 
  mutate(id_digit = as.numeric(str_extract(project_id, "\\d+"))) %>%
  arrange(id_digit) %>% 
  mutate(
    current_ratio = ifelse(currentliabilities == 0, NA, currentasset / currentliabilities),
    dissolved = factor(dissolved),
    employee_owned = factor(`employee-owned`))
```


```{r}
# checking the largest number for the project_id in the finance data set 
summary(finance1$id_digit)
```

```{r}
#merging the data
cic2019 <- rating %>% 
  left_join(finance1, by = "project_id")
```


## data cleanning

```{r}
#select relevant columns, rename and relabel 
cic_cleaned <- cic2019 %>% 
  # recode legal form types to be more readable / easier to present
  mutate(# inherited = ifelse(inherited == "Y", TRUE, FALSE),
         rating = recode(rating, 
                         "Insufficient evidence to rate" = "NA",
                         "Requires improvement" = "Req improv"),
         date = ymd(publication_date)) %>% 
  
  # assign order in the rating levels
  mutate(rating = ordered(rating, levels = c("Inadequate","Req improv", "Good", "Outstanding")),
         social_care = ifelse(type == "Social Care Org", "social care", "healthcare")) %>% 
  
  
  # creating a new dummy variable for facility category
  mutate(founded = as.numeric(founded),
         year = year(date),
         age = year - founded, 
         Year = factor(year)) %>% 
  mutate(cls = ifelse(CLS == 1, "CLS", "CLG"),
         totalequity = as.numeric(totalequity),
         totalequity_std = scale(totalequity, center = TRUE, scale = TRUE)) %>% 
  
   mutate(share_size = case_when(
    totalissueshares <= 20 ~ "small",
    totalissueshares >= 100000 ~ "large",
    TRUE ~ NA_character_
  ))
```
Check the distribution of the data for share_size 

```{r}
cic_cleaned %>% 
  count(share_size)
```




Total counts in full data set

```{r}
count_full <- cic_cleaned %>% 
  mutate(overall = ifelse(domain == "Overall", 1, 0)) %>% 
  summarize(count_provider = n_distinct(provider_name),
            count_location = n_distinct(location_name)-1,
            count_overall_rating = sum(overall),
            count_rating = n()) 

count_full
```

```{r}
count_by_form <- cic_cleaned %>% 
  mutate(overall = ifelse(domain == "Overall", 1, 0)) %>% 
  group_by(cls) %>% 
  summarize(count_provider = n_distinct(provider_name),
            count_location = n_distinct(location_name)-1,
            count_overall_rating = sum(overall),
            count_rating = n()) 

count_by_form
```

```{r}
count_by_level_form <- cic_cleaned %>% 
  mutate(overall = ifelse(domain == "Overall", 1, 0)) %>% 
  group_by(cls, level) %>% 
  summarize(count_provider = n_distinct(provider_name),
            count_location = n_distinct(location_name), 
 # the count_location for provider should be manually adjusted to 0
            count_overall_rating = sum(overall),
            count_rating = n()) 

count_by_level_form
```


```{r}
count_by_level <- cic_cleaned %>% 
  mutate(overall = ifelse(domain == "Overall", 1, 0)) %>% 
  group_by(level) %>% 
  summarize(count_provider = n_distinct(provider_name),
            count_location = n_distinct(location_name), 
 # the count_location for provider should be manually adjusted to 0
            count_overall_rating = sum(overall),
            count_rating = n()) 

count_by_level
```

```{r}
count_by_level_type <- cic_cleaned %>% 
  mutate(overall = ifelse(domain == "Overall", 1, 0)) %>% 
  group_by(social_care, level) %>% 
  summarize(count_provider = n_distinct(provider_name),
            count_location = n_distinct(location_name), 
 # the count_location for provider should be manually adjusted to 0
            count_overall_rating = sum(overall),
            count_rating = n()) 

count_by_level_type
```






```{r}
datasummary_crosstab(
  formula = cls ~ rating,
  data = cic_cleaned
)
```

```{r}
datasummary_crosstab(
  formula = cls * spinout ~ rating,
  data = cic_cleaned
)
```


## regression analysis

### models without finance variable 

```{r }
model_order_overall <- clm(rating ~ cls  + spinout + social_care + age + dissolved,
                data = filter(cic_cleaned, domain == "Overall"),
                link = "logit")

model_order_safe <- clm(rating ~ cls  + spinout + social_care + age + dissolved,
                data = filter(cic_cleaned, domain == "Safe"),
                link = "logit")
model_order_effective <- clm(rating ~ cls  + spinout + social_care + age + dissolved,
                data = filter(cic_cleaned, domain == "Effective"),
                link = "logit")
model_order_caring <- clm(rating ~ cls  + spinout + social_care + age + dissolved,
                data = filter(cic_cleaned, domain == "Caring"),
                link = "logit")
model_order_well_led <- clm(rating ~ cls  + spinout + social_care + age + dissolved,
                data = filter(cic_cleaned, domain == "Well-led"),
                link = "logit")
model_order_responsive <- clm(rating ~ cls  + spinout + social_care + age + dissolved,
                data = filter(cic_cleaned, domain == "Responsive"),
                link = "logit")
```


```{r}
ordinal_models <-
  modelsummary(
    list(
      "overall" = model_order_overall,
      "safe" = model_order_safe,
      "effective" = model_order_effective,
      "caring" = model_order_caring,
      "well-led" = model_order_well_led,
      "responsive" = model_order_responsive
    ),
    coef_omit = "region",
    exponentiate = F,
    statistic = "({p.value}) {stars}")
ordinal_models
```


### model without finance with employee-owned


```{r }
employ_order_overall <- clm(rating ~ cls  + spinout + social_care + age + dissolved + employee_owned,
                data = filter(cic_cleaned, domain == "Overall"),
                link = "logit")

employ_order_safe <- clm(rating ~ cls  + spinout + social_care + age + dissolved + employee_owned,
                data = filter(cic_cleaned, domain == "Safe"),
                link = "logit")
employ_order_effective <- clm(rating ~ cls  + spinout + social_care + age + dissolved + employee_owned,
                data = filter(cic_cleaned, domain == "Effective"),
                link = "logit")
employ_order_caring <- clm(rating ~ cls  + spinout + social_care + age + dissolved + employee_owned,
                data = filter(cic_cleaned, domain == "Caring"),
                link = "logit")
employ_order_well_led <- clm(rating ~ cls  + spinout + social_care + age + dissolved + employee_owned,
                data = filter(cic_cleaned, domain == "Well-led"),
                link = "logit")
employ_order_responsive <- clm(rating ~ cls  + spinout + social_care + age + dissolved + employee_owned,
                data = filter(cic_cleaned, domain == "Responsive"),
                link = "logit")
```

```{r}
employ_models <-
  modelsummary(
    list(
      "overall" = employ_order_overall,
      "safe" = employ_order_safe,
      "effective" = employ_order_effective,
      "caring" = employ_order_caring,
      "well-led" = employ_order_well_led,
      "responsive" = employ_order_responsive
    ),
    coef_omit = "region",
    exponentiate = F,
    statistic = "({p.value}) {stars}")
employ_models
```






### models with equity variables 
```{r}

```

Due to the large range/dispersion of the fiancial data. I standardize the `totalequity` variable to enable the models to run. 

```{r}
summary(cic_cleaned$totalequity)
```

### models with total equity 


```{r }
eq_order_overall <- clm(rating ~ cls  + spinout + social_care + age + dissolved + totalequity_std,
                data = filter(cic_cleaned, domain == "Overall"),
                link = "logit")

eq_order_safe <- clm(rating ~ cls  + spinout + social_care + age + dissolved + totalequity_std,
                data = filter(cic_cleaned, domain == "Safe"),
                link = "logit")
eq_order_effective <- clm(rating ~ cls  + spinout + social_care + age + dissolved + totalequity_std,
                data = filter(cic_cleaned, domain == "Effective"),
                link = "logit")
eq_order_caring <- clm(rating ~ cls  + spinout + social_care + age + dissolved + totalequity_std,
                data = filter(cic_cleaned, domain == "Caring"),
                link = "logit")
eq_order_well_led <- clm(rating ~ cls  + spinout + social_care + age + dissolved + totalequity_std,
                data = filter(cic_cleaned, domain == "Well-led"),
                link = "logit")
eq_order_responsive <- clm(rating ~ cls  + spinout + social_care + age + dissolved + totalequity_std,
                data = filter(cic_cleaned, domain == "Responsive"),
                link = "logit")
```






```{r}
eq_models <-
  modelsummary(
    list(
      "overall" = eq_order_overall,
      "safe" = eq_order_safe,
      "effective" = eq_order_effective,
      "caring" = eq_order_caring,
      "well-led" = eq_order_well_led,
      "responsive" = eq_order_responsive
    ),
    coef_omit = "region",
    exponentiate = F,
    statistic = "({p.value}) {stars}")
eq_models
```



### models with current ratio 



```{r }
current_order_overall <- clm(rating ~ cls  + spinout + social_care + age + dissolved + current_ratio,
                data = filter(cic_cleaned, domain == "Overall"),
                link = "logit")

current_order_safe <- clm(rating ~ cls  + spinout + social_care + age + dissolved + current_ratio,
                data = filter(cic_cleaned, domain == "Safe"),
                link = "logit")
current_order_effective <- clm(rating ~ cls  + spinout + social_care + age + dissolved + current_ratio,
                data = filter(cic_cleaned, domain == "Effective"),
                link = "logit")
current_order_caring <- clm(rating ~ cls  + spinout + social_care + age + dissolved + current_ratio,
                data = filter(cic_cleaned, domain == "Caring"),
                link = "logit")
current_order_well_led <- clm(rating ~ cls  + spinout + social_care + age + dissolved + current_ratio,
                data = filter(cic_cleaned, domain == "Well-led"),
                link = "logit")
current_order_responsive <- clm(rating ~ cls  + spinout + social_care + age + dissolved + current_ratio,
                data = filter(cic_cleaned, domain == "Responsive"),
                link = "logit")
```






```{r}
current_models <-
  modelsummary(
    list(
      "overall" = current_order_overall,
      "safe" = current_order_safe,
      "effective" = current_order_effective,
      "caring" = current_order_caring,
      "well-led" = current_order_well_led,
      "responsive" = current_order_responsive
    ),
    coef_omit = "region",
    exponentiate = F,
    statistic = "({p.value}) {stars}")
current_models
```








