---
title: "Data cleaning 2019 2 levels"
author: "Meng Ye"
date: "2024-06-14"
output: html_document
---

## Introduction 

The current version include the data cleaning for location level CQC data from October 2019. 


### Load packages 

```{r load package, message=FALSE, warning=FALSE}
library(tidyverse) # package for data cleaning and plotting
library(readxl)
library(modelsummary)
set.seed(5432)
```



## 1. Data at the location level 


```{r import data 0, message=FALSE, warning=FALSE}
# import location level full data
locations<- read_excel(here("data","2019_oct_ratings.xlsx"), sheet = 2)
```



### Clean and filter out Gov and CIC providers

```{r rename and filter, message=FALSE, warning=FALSE}
### Rename the columns 

locations_renamed <- locations %>% 
  rename(primary_cat = `Location Primary Inspection Category`,
         type = `Location Type`,
         region = `Location Region`,
         domain = `Domain`, 
         rating = `Latest Rating`,
         inherited = `Inherited Rating (Y/N)`, 
         provider_name = `Provider Name`,
         publication_date = `Publication Date`) 
```



### Standardize the provider name

```{r sample std}
locations_std <- locations_renamed %>% 
# remove dots
  mutate(std_name = str_replace_all(provider_name, "\\.", "")) %>% 
# capitalize all
  mutate(std_name = str_to_upper(std_name)) %>%
# standardize to LTD
  mutate(std_name = str_replace_all(std_name, "LIMITED", "LTD")) %>% 
# standardize to CIC
  mutate(std_name = str_replace_all(std_name, "COMMUNITY INTEREST COMPANY", "CIC"))
```


### filtering out CICs


```{r}
## filtering out CICs and GOVs
locations_coded <- locations_std %>% 
  filter(str_detect(std_name, "CIC")) %>% 
  ## add the form and level columns
  mutate(level = "location")
nrow(locations_coded)
```



```{r}
## re-arrange columns 

locations_to_merge <- locations_coded %>%
  mutate(project_id = paste0("location", row_number())) %>%
  select(
    project_id,
    std_name,
    provider_name,
    location_name = `Location Name`,
    type,
    level,
    service_group = `Service / Population Group`,
    domain,
    rating,
    publication_date,
    primary_cat,
    region,
    report_type = `Report Type`
  )

```


## 2. Data at the provider level 


```{r import data 0, message=FALSE, warning=FALSE}
# sampled data manually coded (with unfriendly column names)
providers <- read_excel(here("data","2019_oct_ratings.xlsx"), sheet = 3)
```


```{r import data, message=FALSE, warning=FALSE}
### Rename the columns 

providers_renamed <- providers %>% 
  rename(primary_cat = `Provider Primary Inspection Category`,
         type = `Provider Type`,
         region = `Provider Region`,
         domain = `Domain`, 
         rating = `Latest Rating`,
         provider_name = `Provider Name`,
         publication_date = `Publication Date`) 
```



### Standardize the provider name

```{r sample std}
providers_std <- providers_renamed %>% 
# remove dots
  mutate(std_name = str_replace_all(provider_name, "\\.", "")) %>% 
# capitalize all
  mutate(std_name = str_to_upper(std_name)) %>%
# standardize to LTD
  mutate(std_name = str_replace_all(std_name, "LIMITED", "LTD")) %>% 
# standardize to CIC
  mutate(std_name = str_replace_all(std_name, "COMMUNITY INTEREST COMPANY", "CIC"))
```


### filtering out CIC and GOV providers


```{r}
## filtering out CICs and GOVs
providers_coded <- providers_std %>% 
  filter(str_detect(std_name, "CIC")) %>% 
  mutate(level = "provider") %>% 
  mutate(location_name = "NA")
nrow(providers_coded)
```

```{r}
## re-arrange columns 

providers_to_merge <- providers_coded %>% 
  mutate(project_id = paste0("provider", row_number())) %>% 
  select(
    project_id,
    std_name,
    provider_name,
    location_name,
    type,
    level,
    service_group = `Service / Population Group`,
    domain,
    rating,
    publication_date,
    primary_cat,
    region,
    report_type = `Report Type`
  )
```




## 3. Merge the two level data 

```{r}
combined_2levels <- bind_rows(locations_to_merge, providers_to_merge)
# prepare data files
cic_all_ratings_2019 <- combined_2levels

cic_overall_ratings_2019 <- combined_2levels %>% 
  filter(domain == "Overall")

```

## save as csv files

```{r}
write_csv(cic_all_ratings_2019, file = here("cleaned_data", "cic_all_ratings_2019.csv"))
write_csv(cic_overall_ratings_2019 , file = here("cleaned_data", "cic_overall_ratings_2019 .csv"))
```


